Toolset for an automated troubleshooting in SDNs

### 2013-11-04 draft.tex
done

\documentclass[10pt,article]{IEEEtran}
\usepackage{cite}
\usepackage[cmex10]{amsmath}
\usepackage{array}
\usepackage{url}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{verbatim}
\usepackage{lmodern}
\usepackage{flushend}
\begin{document}
\title{Automated troubleshooting toolset for SDNs}

@@

\maketitle
\begin{abstract}
In this paper, we propose a methodological review of the existing tools designed for Software-Defined networks troubleshooting. This review is organized using the SDN layering architecture, and aims to show the possibility of an automated localization of the bugs in the different layers of SDN. The toolset presented here allows administrators to more focus on fixing than localizing issues. We will go through the layers by choosing the most significant and relevant tools for each (pair of) layer(s), regarding the other existing tools : NDB for spotting incoherences between policies and their effects, VeriFlow for verifying invariants in real-time, SOFT for spotting bugs in OpenFlow switches configuration, NICE either for the switch firmware of the controller software and FlowChecker supporting verification for different OpenFlow federated infrastructures.
\end{abstract}

>>>>

\documentclass[10pt,article]{IEEEtran}
\usepackage{cite}
\usepackage[cmex10]{amsmath}
\usepackage{array}
\usepackage{url}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{verbatim}
\usepackage{lmodern}
\usepackage{flushend}
\begin{document}
\title{Toolset for an automated troubleshooting in SDNs}

@@

\maketitle
\begin{abstract}
In this paper, we propose a methodological review of the existing tools designed for Software-Defined networks troubleshooting. This review is organized using the SDN layering architecture, and aims to show the possibility of an automated localization of the bugs in the different layers of SDN. The toolset presented here allows administrators to more focus on fixing than localizing issues. We will go through the layers by choosing the most significant and relevant tools for each (pair of) layer(s), regarding other existing tools : NDB for spotting incoherences between policies and their effects, VeriFlow for verifying invariants in real-time, SOFT for spotting bugs in OpenFlow switches configuration, NICE either for the switch firmware of the controller software and FlowChecker supporting verification for different OpenFlow federated infrastructures.
\end{abstract}
